Forecasting the US Election 2024

### 2024-11-02 paper/paper.qmd
update model section

**Model 4**: A Bayesian model implemented using the `rstanarm` package, incorporating the same predictors as Model 3 but allowing for more robust estimation under uncertainty.

@@

-   **Strengths**: The models are interpretable and straightforward, with the Bayesian approach providing a robust framework for uncertainty quantification.
-   **Weaknesses**: Potential oversimplification and assumptions of linearity. Future iterations could explore non-linear effects or hierarchical models.
-   **Final Choice**: We selected **Model 3** (linear model with `end_date`, `pollster`, and `is_national`) for its balance of interpretability and predictive performance. The Bayesian model serves as a robustness check, with results presented in the appendix.

@@

**Results**: Model 3 has the lowest AIC and BIC, suggesting it offers the best balance between goodness-of-fit and complexity. This model includes both time trends and categorical effects for pollsters and national versus state-specific polls.

@@

**Interpretation**: Model 3's residuals suggest that the model adequately captures the data's underlying structure, with no major violations of the linear model assumptions.

>>>>

**Model 4**: A Bayesian model implemented using the `rstanarm` package, incorporating the same predictors as Model 2 but allowing for more robust estimation under uncertainty.

@@

-   **Strengths**: The models are interpretable and straightforward, with the Bayesian approach providing a robust framework for uncertainty quantification.
-   **Weaknesses**: Potential oversimplification and assumptions of linearity. Future iterations could explore non-linear effects or hierarchical models.
-   **Final Choice**: We selected **Model 2** (linear model with `end_date` and `pollster`) for its balance of interpretability and predictive performance. The Bayesian model serves as a robustness check, with results presented in the appendix.

@@

**Results**: Model 2 has the lowest AIC and BIC, suggesting it offers the best balance between goodness-of-fit and complexity. This model includes both time trends and categorical effects for pollsters and national versus state-specific polls.

@@

**Interpretation**: Model 2's residuals suggest that the model adequately captures the data's underlying structure, with no major violations of the linear model assumptions.
